Significant wind disturbances induced by giant dunes.

### 2021-11-19 Paper/main.tex
Adding a new figure for other regime diagrams in SI

  \begin{figure}
    \centering
    \includegraphics[scale=1]{Figures/Figure5.pdf}
    \caption{Regime diagrams of the wind deviation $\delta_{\theta}$ and relative attenuation/amplification $\delta_{u}$, containing the data from both the Deep Sea and South Namib stations. Blue dashed lines empirically delimit the different regimes. The point density in each bin of the diagrams is shown in Fig.~\ref{Fig11_supp}.}
    \label{Fig5}
  \end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=1]{Figures/Figure12_supp.pdf}
  \caption{Physical interpretation of the flow disturbance. (a) and (b) Magnitude of the disturbance induced by a sinusoidal topography calculated from the time series of the non-dimensional numbers presented in Figures~\ref{Fig4} and \ref{Fig5} using the linear model of \citet{andreotti2009}. (c) Shear velocity streamlines represented in the case of the Deep Sea station, for increasing values of $\sqrt{\mathcal{A}_{0}^{2} + \mathcal{B}_{0}^{2}}$. From the upper to the lower streamline, values of $\left(kH,\, Fr_{\textup{surface}},\, Fr_{\textup{internal}},\, \mathcal{A}_{0},\, \mathcal{B}_{0},\, \sqrt{\mathcal{A}_{0}^{2} + \mathcal{B}_{0}^{2}}\right)$ are (1.9, 0.6, 1.5, 3.4, 1.0, 3.5), (1.5, 0.3, 0.4, 4.8, 1.4, 5.0), (0.1, 3.5, 1.0, 8.6, 0.1, 8.6), (0.5, 0.05, 0.04, 9.6, 2.5, 9.9).}
  \label{Fig12_supp}
\end{figure}

>>>>

  \begin{figure}
    \centering
    \includegraphics[scale=1]{Figures/Figure5.pdf}
    \caption{Regime diagrams of the wind deviation $\delta_{\theta}$ and relative attenuation/amplification $\delta_{u}$ in the space $(\mathcal{F}r_{\textup{S}}, \, kH)$, containing the data from both the Deep Sea and South Namib stations. Blue dashed lines empirically delimit the different regimes. The point density in each bin of the diagrams is shown in Fig.~\ref{Fig11_supp}. The regime diagrams in the spaces $(\mathcal{F}r_{\textup{I}}, \, kH)$ and $(\mathcal{F}r_{\textup{I}}, \, \mathcal{F}r_{\textup{S}})$ are shown in Fig.~\ref{Fig12_supp}.}
    \label{Fig5}
  \end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=1]{Figures/Figure12_supp.pdf}
  \caption{Regime diagrams of the wind deviation $\delta_{\theta}$ and relative attenuation/amplification $\delta_{u}$ in the spaces $(\mathcal{F}r_{\textup{I}}, \, kH)$ and $(\mathcal{F}r_{\textup{I}}, \, \mathcal{F}r_{\textup{S}})$, containing the data from both the Deep Sea and South Namib stations. Blue dashed lines empirically delimit the different regimes. The point density in each bin of the diagrams is shown in Fig.~\ref{Fig11_supp}. The regime diagrams in the space $(\mathcal{F}r_{\textup{S}}, \, kH)$ are shown in Fig.~\ref{Fig5_supp}.}
  \label{Fig12_supp}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=1]{Figures/Figure13_supp.pdf}
  \caption{Physical interpretation of the flow disturbance. (a) and (b) Magnitude of the disturbance induced by a sinusoidal topography calculated from the time series of the non-dimensional numbers presented in Figures~\ref{Fig4} and \ref{Fig5} using the linear model of \citet{andreotti2009}. (c) Shear velocity streamlines represented in the case of the Deep Sea station, for increasing values of $\sqrt{\mathcal{A}_{0}^{2} + \mathcal{B}_{0}^{2}}$. From the upper to the lower streamline, values of $\left(kH,\, Fr_{\textup{surface}},\, Fr_{\textup{internal}},\, \mathcal{A}_{0},\, \mathcal{B}_{0},\, \sqrt{\mathcal{A}_{0}^{2} + \mathcal{B}_{0}^{2}}\right)$ are (1.9, 0.6, 1.5, 3.4, 1.0, 3.5), (1.5, 0.3, 0.4, 4.8, 1.4, 5.0), (0.1, 3.5, 1.0, 8.6, 0.1, 8.6), (0.5, 0.05, 0.04, 9.6, 2.5, 9.9).}
  \label{Fig13_supp}
\end{figure}
